---
title: "YG disturbance mapping - scale and resolution"
output:
  html_document:
    keep_md: false
---

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(sf)
library(dplyr)
library(knitr)
```

<br>

Below are some basic summary tables describing the minimum and maximum mapping scale and image resolution used to digitize point, linear, and areal disturbances by the Yukon Government (YG) surface disturbance mapping project. For each feature type (point, linear, areal), the tables are grouped by disturbance type and sensor type.

---

## Point disturbances

### Disturbance type

```{r echo=FALSE, message=FALSE, warning=FALSE}
points <- st_read('C:/Users/PIVER37/Dropbox (BEACONs)/dc_mapping/gisdata/YT/YG_SurfaceDisturbance/YG Surface Disturbance [Most Recent].gdb', 'Point_Features', quiet=T) %>%
    select(SUBTYPE, SCALE, IMAGE_RESOLUTION, IMAGE_SENSOR) %>% st_drop_geometry()
points_type <- group_by(points, SUBTYPE) %>%
    summarize(scale_min = min(SCALE), 
              scale_max = max(SCALE),
              res_min=min(IMAGE_RESOLUTION), 
              res_max=max(IMAGE_RESOLUTION))
kable(points_type)
```

### Image sensor

```{r echo=FALSE, message=FALSE, warning=FALSE}
points_image <- group_by(points, IMAGE_SENSOR) %>%
    summarize(scale_min = min(SCALE), 
              scale_max = max(SCALE),
              res_min=min(IMAGE_RESOLUTION), 
              res_max=max(IMAGE_RESOLUTION))
kable(points_image)
```

---

## Linear disturbances

### Disturbance type

```{r echo=FALSE, message=FALSE, warning=FALSE}
lines <- st_read('C:/Users/PIVER37/Dropbox (BEACONs)/dc_mapping/gisdata/YT/YG_SurfaceDisturbance/YG Surface Disturbance [Most Recent].gdb', 'Linear_Features', quiet=T) %>%
    select(TYPE_DISTURBANCE, WIDTH_M, SCALE, IMAGE_RESOLUTION, IMAGE_SENSOR) %>% st_drop_geometry()
lines_type <- group_by(lines, TYPE_DISTURBANCE) %>%
    summarize(scale_min = min(SCALE), 
              scale_max = max(SCALE),
              res_min=min(IMAGE_RESOLUTION), 
              res_max=max(IMAGE_RESOLUTION))
kable(lines_type)
```

### Image sensor

```{r echo=FALSE, message=FALSE, warning=FALSE}
lines_image <- group_by(lines, IMAGE_SENSOR) %>%
    summarize(scale_min = min(SCALE), 
              scale_max = max(SCALE),
              res_min=min(IMAGE_RESOLUTION), 
              res_max=max(IMAGE_RESOLUTION))
kable(lines_image)
```

### Scale range by resolution

```{r echo=FALSE, message=FALSE, warning=FALSE}
lines <- st_read('C:/Users/PIVER37/Dropbox (BEACONs)/dc_mapping/gisdata/YT/YG_SurfaceDisturbance/YG Surface Disturbance [Most Recent].gdb', 'Linear_Features', quiet=T) %>%
    select(TYPE_DISTURBANCE, WIDTH_M, SCALE, IMAGE_RESOLUTION, IMAGE_SENSOR) %>% st_drop_geometry()
lines_type <- group_by(lines, IMAGE_RESOLUTION) %>%
    summarize(scale_min = min(SCALE), 
              scale_max = max(SCALE))

kable(lines_type)
```

---

## Areal disturbances

### Disturbance type

```{r echo=FALSE, message=FALSE, warning=FALSE}
polys <- st_read('C:/Users/PIVER37/Dropbox (BEACONs)/dc_mapping/gisdata/YT/YG_SurfaceDisturbance/YG Surface Disturbance [Most Recent].gdb', 'Areal_Features', quiet=T) %>%
    select(TYPE_DISTURBANCE, SCALE, IMAGE_RESOLUTION, IMAGE_SENSOR) %>% st_drop_geometry()
polys_type <- group_by(polys, TYPE_DISTURBANCE) %>%
    summarize(scale_min = min(SCALE), 
              scale_max = max(SCALE),
              res_min=min(IMAGE_RESOLUTION), 
              res_max=max(IMAGE_RESOLUTION))
kable(polys_type)
```

### Image sensor

```{r echo=FALSE, message=FALSE, warning=FALSE}
polys_image <- group_by(polys, IMAGE_SENSOR) %>%
    summarize(scale_min = min(SCALE), 
              scale_max = max(SCALE),
              res_min=min(IMAGE_RESOLUTION), 
              res_max=max(IMAGE_RESOLUTION))
kable(polys_image)
```

### Scale range by resolution

```{r echo=FALSE, message=FALSE, warning=FALSE}
polys <- st_read('C:/Users/PIVER37/Dropbox (BEACONs)/dc_mapping/gisdata/YT/YG_SurfaceDisturbance/YG Surface Disturbance [Most Recent].gdb', 'Areal_Features', quiet=T) %>%
    select(TYPE_DISTURBANCE, SCALE, IMAGE_RESOLUTION, IMAGE_SENSOR) %>% st_drop_geometry()
polys_image <- group_by(polys, IMAGE_RESOLUTION) %>%
    summarize(scale_min = min(SCALE), 
              scale_max = max(SCALE))
kable(polys_image)
```